Many-spin entanglement in multiple quantum NMR with a dipolar ordered initial state

### 2020-05-14 manuscript.tex
Fix bugs: references, indexes, typos

In the present article we consider an intermediate temperature case with low Zeemann temperatures and high dipolar ones. 
Nuclear magnetic ordering~\cite{Abragam_1982} is outside our consideration.
Notice also that the two-pulse Broekart-Jeneer experiment~\cite{Jeener_1967} was performed in the high temperature case.
We prove theoretically that the experiment~\cite{Jeener_1967} can be realized also for the intermediate temperature case of the article. 
It was shown~\cite{Doronin_2011} that in the MQ NMR experiment with the dipolar ordered initial state MQ NMR coherences emerge faster 
than in the MQ NMR experiment with the thermal equilibrium initial state in a strong external magnetic field.
It is important for many-spin entanglement investigations, because they are connected with calculations of the second moment of the distribution at MQ NMR coherences. 
It is also very important for an investigation of the spreading correlation~\cite{Baugh_2001,Baum_1986,S_nchez_2014,Munowitz_1987} and localization effects~\cite{Alvarez_2015,Wei_2018}.
At that the spreading rate can be described through out-of-time ordered correlations which are connected with the distribution of MQ NMR coherences.

@@

MQ NMR dynamics in a nanopore governs the Hamiltonian~\cite{Doronin_2019,Doronin_2009} 
%
\begin{equation}
    \label{eq:1}
    H_{\mathrm{MQ}} = - \dfrac{D}{4} \left[
        \left(I^{+}\right)^{2} 
        + \left(I^{-}\right)^{2} 
    \right] ,
\end{equation}
%
where 
%
\begin{equation}
    \label{eq:2}
    I^{\pm} = \sum\limits_{j=1}^{N} I_{j}^{\pm},
\end{equation}
%
$N$ is the number of the spins in the nanopore, $I^{\pm}_{j}$ are the raising or lowering operators of spin $j$, and $D$ is the dipolar coupling constant averaged by the fast molecular diffusion of spin-carrying atoms (molecules) in nanopores.
We underline that the dipolar coupling constant $D$ is the same for all pairs at interacting spins in the nanopore~\cite{Doronin_2019,Doronin_2009}.
The density matrix $\rho(\tau)$ on the preparation period of the MQ NMR experiment~\cite{Baum_1985} can be obtained from the Liouville evolution equation~\cite{Goldman_1970,Abragam_1982} 
%
\begin{equation}
    \label{eq:3}
    i\dfrac{\mathrm{d}\rho(\tau)}{\mathrm{d}\tau} = \left[
    H_\mathrm{MQ},\rho(\tau)
    \right]
\end{equation}
%
with the initial thermodynamic equilibrium density matrix 
%
\begin{equation}
    \label{eq:4}
       \rho(0) = \rho_\mathrm{eq} = \dfrac{1}{Z}
       e^{
            \frac{\hslash \omega}{k} \alpha_\mathrm{z} I_\mathrm{z} 
            + \frac{\hslash }{k} \beta_\mathrm{d} H_\mathrm{dz}
        },
\end{equation}
%
where 
$Z = \mathrm{Tr} \left\{ e^{\frac{\hslash \omega}{k} \alpha_\mathrm{z} I_\mathrm{z} + \frac{\hslash  }{k} \beta_\mathrm{d} H_\mathrm{dz}} \right\}$ is the partition function, 
$\hslash$ and $k$ are the Plank and Boltzmann constants, 
$\omega_{0}$  is the Larmor frequency , $I_\mathrm{z}$ is the operator of the projection of the total spin angular momentum on the z-axis, 
which is directed along the strong external magnetic field,  
$H_\mathrm{dz}$ is the secular part of the dipole-dipole interaction~(DDI).
Hamiltonian in a strong external magnetic field, and $\alpha_\mathrm{z}$, $\beta_\mathrm{d}$ are the inverse Zeemann and dipolar temperatures. 
We will consider the case when the Zeemann temperature is low $({\frac{\hslash \omega}{k} \alpha_\mathrm{z}}\gg 1)$ 
and the dipolar temperature is high $\left( \frac{\hslash{D}}{k}\beta_\mathrm{d} \ll 1\right)$.
For concreteness we suppose that $\omega_{0} = 2\pi \cdot 500 \cdot 10^{6}$~s$^{-1}$ and $D = 2\pi \cdot 10^{4}$~s$^{-1}$.
In Appendix we proved that the two-pulse Broekart-Jeener sequence~\cite{Goldman_1970,Jeener_1967} results in the dipolar ordered state even at the low Zeemann temperature.
The adiabatic demagnetization~\cite{Goldman_1970,Slichter_1961} is the second method of preparing the system in the dipolar ordered state.
Using those methods we can obtain the system in the thermodynamic equilibrium state with the density matrix
%
\begin{equation}
    \label{eq:5}
    \rho_i = \frac{1}{Z_i} e^\frac{\hslash\beta_\mathrm{d}}{k}H_\mathrm{dz}
    \approx \frac{1}{Z_i}(1 + \frac{\hslash\beta_\mathrm{d}}{k} H_\mathrm{dz}),
\end{equation}
%
where the partition function
%
\begin{equation}
    \label{eq:6}
    Z_i = \mathrm{Tr} \left\{ e^\frac{\hslash\beta_\mathrm{d}}{k} H_\mathrm{dz}\right\} \approx 2^{N}.
\end{equation}
%
MQ NMR dynamics in the nanopore will be investigated on the basis of Eq.~(\ref{eq:3}) with the initial state of Eq.~(\ref{eq:5}).
It is also significant that the Hamiltonian $H_{dz}$ is partially averaged by the fast molecular diffusion in the nanopore and the averaged Hamiltonian can be written as \cite{Fel_dman_2004,Doronin_2011}
%
\begin{equation}
    \label{eq:7}
    H_\mathrm{dz} = \dfrac{D}{2} (3 I^{2}_{z} - I^{2}) , % ?
\end{equation}
%
where $I^{2}$ is the square of the spin angular momentum.

@@

The expression~(\ref{eq:8}) for the MQ NMR signal $G(\tau,\phi)$ can be expended in series over the phase increment $\phi$:
%
\begin{equation}
    \begin{split}
        \label{eq:17}
        G(\tau,\phi)  
        & = \mathrm{Tr} \left\{ 
            \rho(\tau) e^{i \phi I_\mathrm{z} }
            \rho(\tau) e^{-i\phi I_\mathrm{z}}
        \right\}  \\
        & = \mathrm{Tr} \left\{ \rho^2(\tau) \right\} 
        - \phi^2 \mathrm{Tr} \left\{ 
            \rho^2(\tau) I^2_\mathrm{z} 
            - (\rho(\tau) I_\mathrm{z})^2
        \right\} 
        + O(\phi^3)
    \end{split}
\end{equation}
%
It is possible to prove~\cite{Girolami_2017} that the quantum Fisher information $F_\mathrm{Q}(\rho,I_\mathrm{z})$~\cite{Helstrom_1969}
%
\begin{equation}
    \label{eq:18}
    F_\mathrm{Q}(\rho,I_\mathrm{z}) \geq 4 \mathrm{Tr} \left\{ \rho^2 I^2_\mathrm{z} - (\rho I_\mathrm{z})^2 \right\}
\end{equation}
%
At the same time, it is easily to verify that $2 \mathrm{Tr} \left\{ \rho^2(\tau) I_\mathrm{z}^2 - \left( \rho(\tau) I_\mathrm{z} \right)^2 \right\}$ equals to the second moment $M_2$ of the distribution of intensities of the MQ NMR coherences~\cite{Khitrin_1997}
%
\begin{equation}
    \label{eq:19}
    M_2 = \sum_{n} n^2 J_n (\tau) ,
\end{equation}
%
where $J_n(\tau)$ ($n=0,\pm 2, \pm 4, \cdots$) is determined by Eq.~(\ref{eq:13}).
Thus, the second moment of the MQ NMR spectrum provides a low bound on the quantum Fisher information $F_\mathrm{Q}(\rho,I_\mathrm{z})$
It was also shown~\cite{T_th_2014,Pezz__2018} that if
%
\begin{equation}
    \label{eq:20}
    F_\mathrm{Q} (\rho,I_\mathrm{z}) > n k^2 + (N - n k)^2,
\end{equation}
%
where $n$ is the integer part of {N/k}, then the system with the density matrix $\rho(\tau)$ is $k+1$-spin entangled~\cite{Pezz__2009,Hyllus_2012,T_th_2012}.
The results of the numerical analysis of many-spin entanglement in the system of spin-carrying molecules (atoms) initially prepared in the dipolar ordered state are presented in the following section.

@@

The time dependence of the quantum Fisher information in the system consisting of 101 spins is presented in Fig.~(\ref{fig:2}) at different temperatures. 
One can see from Fig.~(\ref{fig:2}a) that the only pair entanglement exists at temperature $T=6\cdot10^{-4}$~K.
At the temperature $T=3.2\cdot10^{-4}$ one can see a strip Fig.~(\ref{fig:2}b), in which the inequality~(\ref{eq:20}) can be satisfied when ${32}\leq {k}\leq{46}$.
Thus, there is many-spin entanglement in spin clusters consisting of 33-47 spins at temperature $3.2\cdot10^{-4}$~K.
When the temperature decreases, the width of the strip, in which many-spin entanglement exists, increases. 
At temperature $T=1.6\cdot10^{-4}$~K (Fig.~(\ref{fig:2}c)) clusters of 48-87 entangled spins emerge, and at temperature $T=4.8\cdot10^{-5}$~K (Fig.~(\ref{fig:2}d)) we have 47-92 entangled spins.

@@

\section{Acknowledgements}
This work was performed as a part of a state task, State Registration No. 0089-2019-0002. 
This work was partially supported by the Russian Foundation for Basic Research (Grants Nos. 20-03-00147, 19-32-80004). 
I.L. Acknowledge support from the Advancement of Theoretical Physics and Mathematics BASIS No. 19-1-5-130-1.

@@

Initially the system is in the thermodynamic equilibrium state in the strong external magnetic field with the density matrix
%
\begin{equation}
    \label{eq:a1}
   \sigma_{i} = \dfrac{e^{\beta_\mathrm{d} \omega_{0} I_\mathrm{z}}}{Z_{i}} ,
   \quad
   Z_{i} = \mathrm{Tr}\left\{e^{\beta_\mathrm{d} \omega_{0} I_\mathrm{z}} \right\}
\end{equation}
%
After the first resonance rf x-pulse one has
%
\begin{equation}
    \label{eq:a2}
    \sigma'(0) = e^{ i \frac \pi 2 I_\mathrm{x}}
    \sigma_{i}
    e^{-i \frac \pi 2 I_\mathrm{x}}
    = \dfrac{e^{\beta_\mathrm{d} \omega_{0} I_\mathrm{y}}}{Z_{i}}  .
\end{equation}
%
Then the system evolves freely time $\tau$ 
and one applies the second resonance y-pulse ratating spins by angle $\theta$ around the y-axis of the RRF.
As a result, one obtains that
\begin{equation}
    \label{eq:a3}
    \sigma'(\tau) 
    = \dfrac{
      e^{-i \theta I_\mathrm{y}} e^{-i H_\mathrm{dz} \tau} 
      e^{\beta_\mathrm{d} \omega_{0} I_\mathrm{y}}
      e^{i H_\mathrm{dz} \tau} e^{i \theta I_\mathrm{y}}
    }{Z_{i}}. 
\end{equation}
%
After time $T_2$ ($T_2$ is the spin relaxation time \cite{Goldman_1970}) the system achieves the thermodynamic equilibrium state
\begin{equation}
    \label{eq:a4}
    \sigma_{f} 
    = \dfrac{ e^{\alpha \omega_{0} I_\mathrm{z} + \beta H_\mathrm{dz}} }{Z_f},
\end{equation}
%
where $\alpha$ and $\beta$ are the inverse Zeeman and dipolar temperatures.
It is evident that the system has the single equilibrium state 
and the temperatures $\alpha$ and $\beta$ are also single.
Those temperatures can be obtained from the conservation laws
\begin{align}
    \label{eq:a5}
    \mathrm{Tr} \left\{ I_\mathrm{z} \sigma'(\tau) \right\}
    & = \mathrm{Tr} \left\{ I_\mathrm{z} \sigma_{f}(\tau) \right\}
    \\
    \label{eq:a6}
    \mathrm{Tr} \left\{ H_\mathrm{dz} \sigma'(\tau) \right\}
    & = \mathrm{Tr} \left\{ H_\mathrm{dz} \sigma_{f}(\tau) \right\}
\end{align}
%
One can rewrite $\mathrm{Tr} \left\{ I_\mathrm{z} \sigma'(\tau) \right\}$ as 
%
\begin{multline}
    \label{eq:a7} 
    \tr{I_\mathrm{z} \sigma'(\tau)}
    =  \dfrac{1}{Z_{i}} \tr{
        e^{i \theta \sy} \sz e^{-i \theta \sy}
        e^{-i \hdz \tau} e^{\beta_\mathrm{L} \omega_{0} \sy} e^{i \hdz \tau}
    } 
    \\
    = \dfrac{1}{Z_i} \tr{
        \left( \cos(\theta) \sz - \sin(\theta) \sx \right) 
        e^{-i \hdz \tau} e^{\beta_\mathrm{L} \omega_{0} \sy} e^{i \hdz \tau}
    }
    \\
    = \dfrac{1}{Z_i} \tr{
        e^{-i \pi \sy}  
        \left( \cos(\theta) \sz - \sin(\theta) \sx \right) 
        e^{-i \hdz \tau} e^{\beta_\mathrm{L} \omega_{0} \sy} e^{i \hdz \tau}
        e^{i \pi \sy}  
    }
    \\
    = - \dfrac{1}{Z_i} \tr{
        \left( \cos(\theta) \sz - \sin(\theta) \sx \right) 
        e^{-i \hdz \tau} e^{\beta_\mathrm{L} \omega_{0} \sy} e^{i \hdz \tau} 
    } = 0
\end{multline}
%
In~(\ref{eq:a7} we took into account that $\left[ e^{-i \pi \sy}, \hdz \right] = 0$.
Since we consider the case of a high dipolar temperature it is possible for rewrite~(\ref{eq:a5}) as
\begin{equation}
    \label{eq:a8}
    0 = \dfrac{1}{Z_f} \tr{ \sz e^{\alpha \omega_0 \sz}}
    + \dfrac{\beta}{Z_f} \tr{\sz e^{\alpha \omega_0 \sz} \hdz}.
\end{equation}
%
Notice that $\tr{\sz} = \tr{\sz\hdz} = 0$. It means that $\alpha = 0$ satisfies Eq.~(\ref{eq:5}). 
Thus we obtain the dipolar ordered state in the considered case.

>>>>

In the present article we consider an intermediate temperature case with low Zeemann temperatures and high dipolar ones. 
Nuclear magnetic ordering~\cite{Abragam_1982} is outside our consideration.
Notice also that the two-pulse Broekart-Jeneer experiment~\cite{Jeener_1967} was performed in the high temperature case.
We prove theoretically that the experiment~\cite{Jeener_1967} can be realized also for the intermediate temperature case of the article. 
It was shown~\cite{Doronin_2011} that in the MQ NMR experiment with the dipolar ordered initial state MQ NMR coherences emerge faster 
than in the MQ NMR experiment with the thermal equilibrium initial state in a strong external magnetic field.
It is important for many-spin entanglement investigations, because they are connected with calculations of the second moment of the distribution of MQ NMR coherences. 
It is also very important for an investigation of the spreading correlation~\cite{Baugh_2001,Baum_1986,S_nchez_2014,Munowitz_1987} and localization effects~\cite{Alvarez_2015,Wei_2018}.
At that the spreading rate can be described through out-of-time ordered correlations which are connected with the distribution of MQ NMR coherences.

@@

MQ NMR dynamics in a nanopore governs the Hamiltonian~\cite{Doronin_2019,Doronin_2009} 
%
\begin{equation}
    \label{eq:1}
    H_{\mathrm{MQ}} = - \dfrac{D}{4} \left[
        \left(I^{+}\right)^{2} 
        + \left(I^{-}\right)^{2} 
    \right] ,
\end{equation}
%
where 
%
\begin{equation}
    \label{eq:2}
    I^{\pm} = \sum\limits_{j=1}^{N} I_{j}^{\pm},
\end{equation}
%
$N$ is the number of the spins in the nanopore, $I^{\pm}_{j}$ are the raising or lowering operators of spin $j$, and $D$ is the dipolar coupling constant averaged by the fast molecular diffusion of spin-carrying atoms (molecules) in nanopores.
We underline that the dipolar coupling constant $D$ is the same for all pairs at interacting spins in the nanopore~\cite{Doronin_2019,Doronin_2009}.
The density matrix $\rho(\tau)$ on the preparation period of the MQ NMR experiment~\cite{Baum_1985} can be obtained from the Liouville evolution equation~\cite{Goldman_1970,Abragam_1982} 
%
\begin{equation}
    \label{eq:3}
    i\dfrac{\mathrm{d}\rho(\tau)}{\mathrm{d}\tau} = \left[
    H_\mathrm{MQ},\rho(\tau)
    \right]
\end{equation}
%
with the initial thermodynamic equilibrium density matrix 
%
\begin{equation}
    \label{eq:4}
       \rho(0) = \rho_\mathrm{eq} = \dfrac{1}{Z}
       e^{
            \frac{\hslash \omega}{k} \alpha_\mathrm{z} I_\mathrm{z} 
            + \frac{\hslash }{k} \beta_\mathrm{d} H_\mathrm{dz}
        },
\end{equation}
%
where 
$Z = \mathrm{Tr} \left\{ e^{\frac{\hslash \omega}{k} \alpha_\mathrm{z} I_\mathrm{z} + \frac{\hslash  }{k} \beta_\mathrm{d} H_\mathrm{dz}} \right\}$ is the partition function, 
$\hslash$ and $k$ are the Plank and Boltzmann constants, 
$\omega_{0}$  is the Larmor frequency , $I_\mathrm{z}$ is the operator of the projection of the total spin angular momentum on the z-axis, 
which is directed along the strong external magnetic field,  
$H_\mathrm{dz}$ is the secular part of the dipole-dipole interaction~(DDI) Hamiltonian in a strong external magnetic field, and $\alpha_\mathrm{z}$, $\beta_\mathrm{d}$ are the inverse Zeemann and dipolar temperatures. 
We will consider the case when the Zeemann temperature is low $({\frac{\hslash \omega}{k} \alpha_\mathrm{z}}\gg 1)$ 
and the dipolar temperature is high $\left( \frac{\hslash{D}}{k}\beta_\mathrm{d} \ll 1\right)$.
For concreteness we suppose that $\omega_{0} = 2\pi \cdot 500 \cdot 10^{6}$~s$^{-1}$ and $D = 2\pi \cdot 10^{4}$~s$^{-1}$.
In Appendix we proved that the two-pulse Broekart-Jeener sequence~\cite{Goldman_1970,Jeener_1967} results in the dipolar ordered state even at the low Zeemann temperature.
The adiabatic demagnetization~\cite{Goldman_1970,Slichter_1961} is the second method of preparing the system in the dipolar ordered state.
Using those methods we can obtain the system in the thermodynamic equilibrium state with the density matrix
%
\begin{equation}
    \label{eq:5}
    \rho_i = \frac{1}{Z_i} e^\frac{\hslash\beta_\mathrm{d}}{k}H_\mathrm{dz}
    \approx \frac{1}{Z_i}(1 + \frac{\hslash\beta_\mathrm{d}}{k} H_\mathrm{dz}),
\end{equation}
%
where the partition function
%
\begin{equation}
    \label{eq:6}
    Z_i = \mathrm{Tr} \left\{ e^\frac{\hslash\beta_\mathrm{d}}{k} H_\mathrm{dz}\right\} \approx 2^{N}.
\end{equation}
%
MQ NMR dynamics in the nanopore will be investigated on the basis of Eq.~(\ref{eq:3}) with the initial state of Eq.~(\ref{eq:5}).
It is also significant that the Hamiltonian $H_{dz}$ is partially averaged by the fast molecular diffusion in the nanopore and the averaged Hamiltonian can be written as \cite{Fel_dman_2004,Doronin_2011}
%
\begin{equation}
    \label{eq:7}
    H_\mathrm{dz} = \dfrac{D}{2} (3 I^{2}_{z} - I^{2}) , % ?
\end{equation}
%
where $I^{2}$ is the square of the spin angular momentum.

@@

The expression~(\ref{eq:8}) for the MQ NMR signal $G(\tau,\phi)$ can be expanded in series over the phase increment $\phi$:
%
\begin{equation}
    \begin{split}
        \label{eq:17}
        G(\tau,\phi)  
        & = \mathrm{Tr} \left\{ 
            \rho(\tau) e^{i \phi I_\mathrm{z} }
            \rho(\tau) e^{-i\phi I_\mathrm{z}}
        \right\}  \\
        & = \mathrm{Tr} \left\{ \rho^2(\tau) \right\} 
        - \phi^2 \mathrm{Tr} \left\{ 
            \rho^2(\tau) I^2_\mathrm{z} 
            - (\rho(\tau) I_\mathrm{z})^2
        \right\} 
        + O(\phi^3)
    \end{split}
\end{equation}
%
It is possible to prove~\cite{Girolami_2017} that the quantum Fisher information $F_\mathrm{Q}(\rho,I_\mathrm{z})$~\cite{Helstrom_1969}
%
\begin{equation}
    \label{eq:18}
    F_\mathrm{Q}(\rho,I_\mathrm{z}) \geq 4 \mathrm{Tr} \left\{ \rho^2 I^2_\mathrm{z} - (\rho I_\mathrm{z})^2 \right\}
\end{equation}
%
At the same time, it is easily to verify that $2 \mathrm{Tr} \left\{ \rho^2(\tau) I_\mathrm{z}^2 - \left( \rho(\tau) I_\mathrm{z} \right)^2 \right\}$ equals to the second moment $M_2$ of the distribution of intensities of the MQ NMR coherences~\cite{Khitrin_1997}
%
\begin{equation}
    \label{eq:19}
    M_2 = \sum_{n} n^2 J_n (\tau) ,
\end{equation}
%
where $J_n(\tau)$ ($n=0,\pm 2, \pm 4, \cdots$) is determined by Eq.~(\ref{eq:13}).
Thus, the second moment of the MQ NMR spectrum provides a low bound on the quantum Fisher information $F_\mathrm{Q}(\rho,I_\mathrm{z})$
It was also shown~\cite{T_th_2014,Pezz__2018} that if
%
\begin{equation}
    \label{eq:20}
    F_\mathrm{Q} (\rho,I_\mathrm{z}) > n k^2 + (N - n k)^2,
\end{equation}
%
where $n$ is the integer part of {N/k}, then the system with the density matrix $\rho(\tau)$ is $k+1$-spin entangled~\cite{Pezz__2009,Hyllus_2012,T_th_2012}.
The results of the numerical analysis of many-spin entanglement in the system of spin-carrying molecules (atoms) initially prepared in the dipolar ordered state are presented in the following section.

@@

The time dependence of the quantum Fisher information in the system consisting of 101 spins is presented in Fig.~(\ref{fig:2}) at different temperatures. 
One can see from Fig.~(\ref{fig:2}a) that only the pair entanglement exists at temperature $T=6\cdot10^{-4}$~K.
At the temperature $T=3.2\cdot10^{-4}$ one can see a strip Fig.~(\ref{fig:2}b), in which the inequality~(\ref{eq:20}) can be satisfied when ${32}\leq {k}\leq{46}$.
Thus, there is many-spin entanglement in spin clusters consisting of 33-47 spins at temperature $3.2\cdot10^{-4}$~K.
When the temperature decreases, the width of the strip, in which many-spin entanglement exists, increases. 
At temperature $T=1.6\cdot10^{-4}$~K (Fig.~(\ref{fig:2}c)) clusters of 48-87 entangled spins emerge, and at temperature $T=4.8\cdot10^{-5}$~K (Fig.~(\ref{fig:2}d)) we have 47-92 entangled spins.

@@

\section{Acknowledgements}
This work was performed as a part of a state task, State Registration No. 0089-2019-0002. 
This work was partially supported by the Russian Foundation for Basic Research (Grants Nos. 20-03-00147, 19-32-80004). 
I.L. acknowledges support from the Advancement of Theoretical Physics and Mathematics BASIS No. 19-1-5-130-1.

@@

Initially the system is in the thermodynamic equilibrium state in the strong external magnetic field with the density matrix
%
\begin{equation}
    \label{eq:a1}
   \sigma_{i} = \dfrac{e^{\beta_\mathrm{L} \omega_{0} I_\mathrm{z}}}{Z_{i}} ,
   \quad
   Z_{i} = \mathrm{Tr}\left\{e^{\beta_\mathrm{L} \omega_{0} I_\mathrm{z}} \right\}
\end{equation}
%
After the first resonance rf x-pulse one has
%
\begin{equation}
    \label{eq:a2}
    \sigma'(0) = e^{ i \frac \pi 2 I_\mathrm{x}}
    \sigma_{i}
    e^{-i \frac \pi 2 I_\mathrm{x}}
    = \dfrac{e^{\beta_\mathrm{L} \omega_{0} I_\mathrm{y}}}{Z_{i}}  .
\end{equation}
%
Then the system evolves freely time $\tau$ 
and one applies the second resonance y-pulse rotating spins by angle $\theta$ around the y-axis of the RRF.
As a result, one obtains that
\begin{equation}
    \label{eq:a3}
    \sigma'(\tau) 
    = \dfrac{
      e^{-i \theta I_\mathrm{y}} e^{-i H_\mathrm{dz} \tau} 
      e^{\beta_\mathrm{L} \omega_{0} I_\mathrm{y}}
      e^{i H_\mathrm{dz} \tau} e^{i \theta I_\mathrm{y}}
    }{Z_{i}}. 
\end{equation}
%
After time $T_2$ ($T_2$ is the spin relaxation time \cite{Goldman_1970}) the system achieves the thermodynamic equilibrium state
\begin{equation}
    \label{eq:a4}
    \sigma_{f} 
    = \dfrac{ e^{\alpha \omega_{0} I_\mathrm{z} + \beta H_\mathrm{dz}} }{Z_f},
\end{equation}
%
where $\alpha$ and $\beta$ are the inverse Zeeman and dipolar temperatures.
It is evident that the system has the single equilibrium state 
and the temperatures $\alpha$ and $\beta$ are also single.
Those temperatures can be obtained from the conservation laws
\begin{align}
    \label{eq:a5}
    \mathrm{Tr} \left\{ I_\mathrm{z} \sigma'(\tau) \right\}
    & = \mathrm{Tr} \left\{ I_\mathrm{z} \sigma_{f}(\tau) \right\}
    \\
    \label{eq:a6}
    \mathrm{Tr} \left\{ H_\mathrm{dz} \sigma'(\tau) \right\}
    & = \mathrm{Tr} \left\{ H_\mathrm{dz} \sigma_{f}(\tau) \right\}
\end{align}
%
One can rewrite $\mathrm{Tr} \left\{ I_\mathrm{z} \sigma'(\tau) \right\}$ as 
%
\begin{multline}
    \label{eq:a7} 
    \tr{I_\mathrm{z} \sigma'(\tau)}
    =  \dfrac{1}{Z_{i}} \tr{
        e^{i \theta \sy} \sz e^{-i \theta \sy}
        e^{-i \hdz \tau} e^{\beta_\mathrm{L} \omega_{0} \sy} e^{i \hdz \tau}
    } 
    \\
    = \dfrac{1}{Z_i} \tr{
        \left( \cos(\theta) \sz - \sin(\theta) \sx \right) 
        e^{-i \hdz \tau} e^{\beta_\mathrm{L} \omega_{0} \sy} e^{i \hdz \tau}
    }
    \\
    = \dfrac{1}{Z_i} \tr{
        e^{-i \pi \sy}  
        \left( \cos(\theta) \sz - \sin(\theta) \sx \right) 
        e^{-i \hdz \tau} e^{\beta_\mathrm{L} \omega_{0} \sy} e^{i \hdz \tau}
        e^{i \pi \sy}  
    }
    \\
    = - \dfrac{1}{Z_i} \tr{
        \left( \cos(\theta) \sz - \sin(\theta) \sx \right) 
        e^{-i \hdz \tau} e^{\beta_\mathrm{L} \omega_{0} \sy} e^{i \hdz \tau} 
    } = 0
\end{multline}
%
In~(\ref{eq:a7} we took into account that $\left[ e^{-i \pi \sy}, \hdz \right] = 0$.
Since we consider the case of a high dipolar temperature it is possible for rewrite~(\ref{eq:a5}) as
\begin{equation}
    \label{eq:a8}
    0 = \dfrac{1}{Z_f} \tr{ \sz e^{\alpha \omega_0 \sz}}
    + \dfrac{\beta}{Z_f} \tr{\sz e^{\alpha \omega_0 \sz} \hdz}.
\end{equation}
%
Notice that $\tr{\sz} = \tr{\sz\hdz} = 0$. It means that $\alpha = 0$ satisfies Eq.~(\ref{eq:5}). 
Thus we obtain the dipolar ordered state in the considered case.
